Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-12 main_paper.tex
update the simulation table
1. fix the DGP of heteroskedastic data (now keep the average variance at
0.1295^2, not keep the average standard deviation at 0.1295).
2. use default variance estimator (nearest neighbours) in the two
analytical procedures.

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
      & CCT            & --0.011 & 0.067 & 0.068 & 0.928 & 0.247 \\ 
      & Naive          & --0.037 & 0.041 & 0.055 & 0.835 & 0.155 \\ 
    2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
      & CCT            & --0.008 & 0.086 & 0.086 & 0.942 & 0.346 \\
      & Naive          & --0.145 & 0.065 & 0.159 & 0.353 & 0.241 \\
    3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
      & CCT            & --0.005 & 0.065 & 0.065 & 0.945 & 0.253 \\ 
      & Naive          &   0.034 & 0.051 & 0.061 & 0.862 & 0.191 \\ \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & --0.010 & 0.080 & 0.081 & 0.934 & 0.301 \\
      & CCT            & --0.010 & 0.080 & 0.081 & 0.936 & 0.301 \\
      & Naive          & --0.035 & 0.050 & 0.061 & 0.863 & 0.185 \\ 
    2 & Wild bootstrap & --0.008 & 0.094 & 0.095 & 0.921 & 0.351 \\ 
      & CCT            & --0.008 & 0.094 & 0.095 & 0.924 & 0.366 \\
      & Naive          & --0.145 & 0.072 & 0.162 & 0.398 & 0.255 \\  
    3 & Wild bootstrap & --0.001 & 0.103 & 0.103 & 0.942 & 0.396 \\ 
      & CCT            & --0.001 & 0.103 & 0.103 & 0.942 & 0.395 \\ 
      & Naive          &   0.036 & 0.073 & 0.081 & 0.859 & 0.251 \\  
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \begin{tabular}{rlrrrrrrr}
    \toprule
    DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
    \midrule                                                     \\
    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
    \midrule
    1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
      & CCT            & --0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\ 
      & Naive          & --0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\ 
    2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
      & CCT            & --0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\ 
      & Naive          & --0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\ 
    3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
      & CCT            & --0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\ 
      & Naive          &   0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
    \midrule
    1 & Wild bootstrap & --0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
      & CCT            & --0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\ 
      & Naive          & --0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\ 
    2 & Wild bootstrap & --0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\ 
      & CCT            & --0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\ 
      & Naive          & --0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\ 
    3 & Wild bootstrap & --0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\ 
      & CCT            & --0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\ 
      & Naive          &   0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\  
    \bottomrule
  \end{tabular}
  \caption{%
    Experimental coverage probabilities for each interval estimator based on 5000
    simulations; nominal coverage probabilities are 95\% for each estimator. The column
    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
    lists the average length of the confidence interval across simulations.}
  \label{tbl:1}
\end{table}
